\documentclass[a4paper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{fontawesome}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[label={}, leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[label={}]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%---------------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{{\Large Craig Lawrence}} & \faEnvelope \, \href{mailto:craiglawrence198@gmail.com}{craiglawrence198@gmail.com}\\
    \faLinkedin \, \href{https://www.linkedin.com/in/craigjlawrence/}{craigjlawrence} \hspace{2.5mm} \faGithub \, \href{https://github.com/CraigLawrence}{CraigLawrence} & \faMobile \, +61 405 705 725\\
\end{tabular*}

%-----------EDUCATION-----------------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{University of Adelaide}{Adelaide, Australia}
{Bachelor of Software Engineering (First-class honours); GPA: 6.3}{2011 - 2014}
\resumeItemListStart
\resumeItem{Awards}
    {2013 Maptek Prize for the School of Computer Science}
\resumeItemListEnd
\resumeSubHeadingListEnd

%-----------WORK EXPERIENCE-----------
\section{Work Experience}
\resumeSubHeadingListStart
\resumeSubheading
{Binary Group Services}{Cyberjaya, Malaysia}
{Backend Developer}{Dec 2017 - Present}
\resumeItemListStart
\resumeItem{Trading platform}
    {Generally responsible for developing and maintaining Binary's options trading platform. Working in Perl and Progres SQL.}
\resumeItem{GDPR compliance}
    {Travelled to Malta to work directly with the European compliance team on preparing our database for complying with the EU's General Data Protection Regulation}
\resumeItem{Compliance automation}
    {Working with the compliance team to automate current long manual processes. Requires integration of multiple components including Perl modules, Postgres functions, and cron jobs.}
\resumeItem{Pricing engine}
    {Worked in a small group to prototype a new pricing engine written in modern C++. Configured Conan packages, upgraded futures code to C++14 standard, and prepared production Docker container.}
\resumeItem{Configuration management}
    {Rewrote application configuration chronicle to replace monolithic tree structure with key-value system, and enable easier/faster data lookup.}
\resumeItem{ORM migration}
    {Worked on migrating system away from Rose ORM to Moose modules}
\resumeItem{Document API}
    {Improved handling of user submitted documents by preventing duplicate uploads.}
\resumeItem{Recruitment}
    {Proctored hackathons for potential new hires in the backend department.}
\resumeItemListEnd
\resumeSubheading
{DXC Technology (formerly CSC Australia)}{Adelaide, Australia}
{Associate Consultant: Technical}{Feb 2015 - Nov 2017}
\resumeItemListStart
\resumeItem{Legacy migration}
    {Migrating the development/build environment for a legacy Windows 9-x era application to a modern Windows platform, and developing unit tests.}
\resumeItem{Requirements management}
    {Built an internal tool for managing and tracing requirements on Commonwealth contracts. Automated the generation of tables and matrices which previously required hours of manual work.}
\resumeItem{Logistics tool}
    {Tool for managing the movement of physical assets in a government department. Implemented new features and bug fixes in large legacy Java codebase. Wrote automated integration tests.}
\resumeItemListEnd
\resumeSubheading
{Saab Systems}{Adelaide, Australia}
{Undergraduate Software Engineer}{Nov 2013 - Feb 2014}
\resumeItemListStart
\resumeItem{Front-end}
    {Implemented UI improvements for a WPF/C\# application.}
\resumeItem{Testing}
    {Prepared acceptance tests for a prison security software package.}
\resumeItemListEnd
\resumeSubHeadingListEnd

%-----------PROJECTS------------------
\section{Projects}
\resumeSubHeadingListStart
\resumeItem{Breadcrumbs (for Airborne Research Australia)}
    {A C++ application for tracking ground covered by airborne scientific instruments. I developed the algorithm for interpreting the GPS data. I also created plugins for Microsoft Flight Simulator X to aid testing.}
\resumeItem{RFID-PAM}
    {Co-developed a RFID authentication module for Ubuntu. I wrote the Arudino code and PC-side driver for I/O with the device.}
\resumeItem{Reptar (for South Australian Museum)}
    {A web application for cataloguing and searching the museum's CT scans.}
\resumeItem{FrontDoor (for the University of Adelaide School of Computer Science)}
    {A Ruby of Rails application for scheduling casual teaching staff. Developed the front-end and co-designed a genetic optimisation algorithm}
\resumeSubHeadingListEnd

%-----------VOLUNTEERING--------------
\section{Volunteering}
\resumeSubHeadingListStart
\resumeItem{Robocup Junior Australia}
    {Robocup Junior is an organisation dedicating to getting primary and secondary students involved in robotics and technology. I served as a volunteer official at the 2015 Australian Open competition.}
\resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
